---
title: "15 Stories from Virginia School Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{15 Stories from Virginia School Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# Check if VDOE enrollment data is fetchable (CAPTCHA may block)
can_fetch_enr <- tryCatch({
  test_data <- vaschooldata::fetch_enr(2024, tidy = FALSE, use_cache = TRUE)
  is.data.frame(test_data) && nrow(test_data) > 0
}, error = function(e) FALSE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 5,
  cache = TRUE
)
```

```{r load-packages, eval=TRUE}
library(vaschooldata)
library(dplyr)
library(tidyr)
library(ggplot2)

theme_set(theme_minimal(base_size = 14))
```

Virginia educates nearly **1.25 million students** across 132 school divisions and graduates over **90,000 seniors** each year. This package provides 9 years of enrollment data (2016-2024) and 5 years of graduation data (2019-2023) directly from the Virginia Department of Education. Here are fifteen stories hiding in the data.

---

## 1. Virginia graduates 92% of its students

Virginia's four-year graduation rate has held steady between 91.6% and 93.0% over five years, placing it well above the national average of roughly 87%.

```{r grad-trend}
all_grad <- bind_rows(lapply(2019:2023, function(yr) {
  fetch_graduation(yr, use_cache = TRUE)
}))

state_grad <- all_grad |>
  filter(is_state, diploma_type == "all") |>
  select(end_year, graduation_rate, cohort_size, total_graduates, dropout_rate)

state_grad |>
  mutate(grad_pct = round(graduation_rate * 100, 2),
         dropout_pct = round(dropout_rate * 100, 2))
```

```{r grad-trend-chart}
stopifnot(nrow(state_grad) > 0)

ggplot(state_grad, aes(x = end_year, y = graduation_rate)) +
  geom_line(linewidth = 1.2, color = "#003366") +
  geom_point(size = 3, color = "#003366") +
  scale_y_continuous(labels = scales::percent, limits = c(0.88, 0.96)) +
  labs(
    title = "Virginia 4-Year Graduation Rate (2019-2023)",
    subtitle = "Consistently above 91%, peaking in 2021",
    x = "Cohort Year",
    y = "Graduation Rate"
  )
```

---

## 2. More than half of Virginia graduates earn Advanced Studies diplomas

In 2023, 50,175 graduates (54.6% of all diploma recipients) earned the Advanced Studies diploma, Virginia's most rigorous option requiring additional math, science, and foreign language credits. Only 38.3% earned the Standard diploma.

```{r diploma-breakdown}
diplomas <- all_grad |>
  filter(is_state, end_year == 2023, diploma_type != "all", !is.na(diploma_count)) |>
  select(diploma_type, diploma_count) |>
  mutate(pct = round(diploma_count / sum(diploma_count) * 100, 1)) |>
  arrange(desc(diploma_count))

diplomas
```

```{r diploma-breakdown-chart}
stopifnot(nrow(diplomas) > 0)

diplomas |>
  mutate(diploma_type = forcats::fct_reorder(diploma_type, diploma_count)) |>
  ggplot(aes(x = diploma_count, y = diploma_type)) +
  geom_col(fill = "#003366") +
  geom_text(aes(label = paste0(pct, "%")), hjust = -0.1, size = 3.5) +
  scale_x_continuous(labels = scales::comma, expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Virginia Diplomas by Type (2023)",
    subtitle = "Advanced Studies is the most common diploma",
    x = "Number of Graduates",
    y = NULL
  )
```

---

## 3. Richmond City's graduation crisis

Richmond City Public Schools graduates just 72% of its students, the lowest rate among Virginia's 130 school divisions. Its dropout rate of 24% is more than four times the state average of 5.4%.

```{r richmond-grad}
div_grad_23 <- all_grad |>
  filter(is_school, diploma_type == "all", end_year == 2023) |>
  group_by(division_name) |>
  summarize(
    n_schools = n(),
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    dropouts = sum(dropouts, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  )

richmond_trend <- all_grad |>
  filter(is_school, diploma_type == "all", division_name == "Richmond City") |>
  group_by(end_year) |>
  summarize(
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    dropouts = sum(dropouts, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  )

richmond_trend |>
  mutate(grad_pct = round(grad_rate * 100, 1))
```

```{r richmond-grad-chart}
stopifnot(nrow(richmond_trend) > 0)

ggplot(richmond_trend, aes(x = end_year, y = grad_rate)) +
  geom_line(linewidth = 1.2, color = "#B22222") +
  geom_point(size = 3, color = "#B22222") +
  geom_hline(yintercept = 0.9193, linetype = "dashed", alpha = 0.5) +
  annotate("text", x = 2022, y = 0.93, label = "State average (91.9%)", size = 3.5) +
  scale_y_continuous(labels = scales::percent, limits = c(0.65, 0.96)) +
  labs(
    title = "Richmond City Graduation Rate (2019-2023)",
    subtitle = "Persistently below state average, with a brief COVID-era bump",
    x = "Cohort Year",
    y = "Graduation Rate"
  )
```

---

## 4. Loudoun County leads Northern Virginia in graduation rates

Among NoVA's four largest divisions, Loudoun County consistently graduates the highest share of students at 96.7%, followed by Arlington (93.5%), Fairfax (93.4%), and Prince William (91.7%).

```{r nova-grad}
nova_grad <- all_grad |>
  filter(is_school, diploma_type == "all",
         division_name %in% c("Fairfax County", "Loudoun County",
                               "Prince William County", "Arlington County")) |>
  group_by(end_year, division_name) |>
  summarize(
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  )

nova_grad |>
  filter(end_year == 2023) |>
  arrange(desc(grad_rate)) |>
  mutate(grad_pct = round(grad_rate * 100, 1))
```

```{r nova-grad-chart}
stopifnot(nrow(nova_grad) > 0)

ggplot(nova_grad, aes(x = end_year, y = grad_rate, color = division_name)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(labels = scales::percent, limits = c(0.88, 1.0)) +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Northern Virginia Graduation Rates (2019-2023)",
    subtitle = "Loudoun County leads the region",
    x = "Cohort Year",
    y = "Graduation Rate",
    color = "Division"
  )
```

---

## 5. COVID drove dropout rates to a five-year low

Virginia's dropout rate fell from 5.5% in 2019 to 4.3% in 2021, possibly reflecting emergency pandemic policies that kept students enrolled. By 2023, dropout rates had rebounded to 5.4%.

```{r covid-dropout}
dropout_trend <- all_grad |>
  filter(is_state, diploma_type == "all") |>
  select(end_year, graduation_rate, dropout_rate) |>
  mutate(
    grad_pct = round(graduation_rate * 100, 2),
    dropout_pct = round(dropout_rate * 100, 2)
  )

dropout_trend
```

```{r covid-dropout-chart}
stopifnot(nrow(dropout_trend) > 0)

ggplot(dropout_trend, aes(x = end_year, y = dropout_rate)) +
  geom_line(linewidth = 1.2, color = "#D32F2F") +
  geom_point(size = 3, color = "#D32F2F") +
  geom_vline(xintercept = 2021, linetype = "dashed", alpha = 0.5) +
  annotate("text", x = 2021.3, y = 0.052, label = "2021\npandemic\npolicies", size = 3) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Virginia Statewide Dropout Rate (2019-2023)",
    subtitle = "Pandemic-era policies temporarily reduced dropouts",
    x = "Cohort Year",
    y = "Dropout Rate"
  )
```

---

## 6. Thomas Jefferson: Virginia's 100% graduation factory

Thomas Jefferson High School for Science and Technology (TJHSST) in Fairfax County has graduated 100% of its cohort for four consecutive years (2020-2023). With 459 students in its 2023 cohort, it is the largest school in Virginia with a perfect graduation rate.

```{r tj-trend}
tj <- all_grad |>
  filter(is_school, diploma_type == "all",
         grepl("Thomas Jefferson High for Science", school_name)) |>
  select(end_year, school_name, graduation_rate, cohort_size)

tj
```

```{r perfect-schools}
perfect <- all_grad |>
  filter(is_school, diploma_type == "all", end_year == 2023,
         graduation_rate == 1.0, cohort_size >= 30) |>
  select(school_name, division_name, cohort_size) |>
  arrange(desc(cohort_size))

perfect
```

---

## 7. Hampton Roads: Norfolk is the outlier

Among Hampton Roads' five largest divisions, Norfolk City graduates just 82% of its students, lagging 10+ points behind neighbors like Hampton City (96.4%) and Virginia Beach (95.3%).

```{r hampton-roads-grad}
hr_divisions <- c("Virginia Beach City", "Norfolk City",
                   "Newport News City", "Hampton City", "Chesapeake City")

hr_grad <- all_grad |>
  filter(is_school, diploma_type == "all",
         division_name %in% hr_divisions) |>
  group_by(end_year, division_name) |>
  summarize(
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  )

hr_grad |>
  filter(end_year == 2023) |>
  arrange(desc(grad_rate)) |>
  mutate(grad_pct = round(grad_rate * 100, 1))
```

```{r hampton-roads-grad-chart}
stopifnot(nrow(hr_grad) > 0)

ggplot(hr_grad, aes(x = end_year, y = grad_rate, color = division_name)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(labels = scales::percent, limits = c(0.75, 1.0)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Hampton Roads Graduation Rates (2019-2023)",
    subtitle = "Norfolk City trails the region by a wide margin",
    x = "Cohort Year",
    y = "Graduation Rate",
    color = "Division"
  )
```

---

## 8. Southwest Virginia coalfield schools defy decline narratives

Despite losing population, Southwest Virginia's rural schools maintain strong graduation rates. Wise County graduates 98.3% of its students, higher than Fairfax County (93.4%) or any other NoVA division.

```{r swva-grad}
swva_divisions <- c("Lee County", "Dickenson County", "Buchanan County",
                     "Wise County", "Tazewell County")

swva_grad <- all_grad |>
  filter(is_school, diploma_type == "all",
         division_name %in% swva_divisions) |>
  group_by(end_year, division_name) |>
  summarize(
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  )

swva_grad |>
  filter(end_year == 2023) |>
  arrange(desc(grad_rate)) |>
  mutate(grad_pct = round(grad_rate * 100, 1))
```

```{r swva-grad-chart}
stopifnot(nrow(swva_grad) > 0)

ggplot(swva_grad, aes(x = end_year, y = grad_rate, color = division_name)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_y_continuous(labels = scales::percent, limits = c(0.75, 1.0)) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "Southwest Virginia Coalfield Graduation Rates (2019-2023)",
    subtitle = "Small coalfield divisions graduate at high rates despite population loss",
    x = "Cohort Year",
    y = "Graduation Rate",
    color = "Division"
  )
```

---

## 9. Virginia's largest high schools are all in Northern Virginia

Alexandria City High School leads the state with 1,138 seniors in its 2023 cohort. Eight of the ten largest high schools are in Fairfax, Prince William, or Arlington counties.

```{r largest-schools}
big_schools <- all_grad |>
  filter(is_school, diploma_type == "all", end_year == 2023) |>
  arrange(desc(cohort_size)) |>
  select(school_name, division_name, cohort_size, graduation_rate) |>
  head(10) |>
  mutate(grad_pct = round(graduation_rate * 100, 1))

big_schools
```

```{r largest-schools-chart}
stopifnot(nrow(big_schools) > 0)

big_schools |>
  mutate(school_label = paste0(school_name, " (", division_name, ")"),
         school_label = forcats::fct_reorder(school_label, cohort_size)) |>
  ggplot(aes(x = cohort_size, y = school_label)) +
  geom_col(fill = "#003366") +
  geom_text(aes(label = paste0(grad_pct, "%")), hjust = -0.1, size = 3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Virginia's 10 Largest High Schools by Cohort (2023)",
    subtitle = "Labels show graduation rate",
    x = "Cohort Size",
    y = NULL
  )
```

---

## 10. Virginia loses 5,300 students to dropout every year

Over the 2019-2023 period, Virginia averaged roughly 5,000 dropouts per year. The 2021 pandemic-policy dip to 4,129 was temporary; 2023 saw 5,319 dropouts.

```{r dropout-count}
dropout_counts <- all_grad |>
  filter(is_state, diploma_type == "all") |>
  select(end_year, cohort_size, total_graduates, dropouts, still_enrolled) |>
  mutate(
    dropout_pct = round(dropouts / cohort_size * 100, 1),
    still_enrolled_pct = round(still_enrolled / cohort_size * 100, 1)
  )

dropout_counts
```

```{r dropout-count-chart}
stopifnot(nrow(dropout_counts) > 0)

dropout_long <- dropout_counts |>
  select(end_year, Dropouts = dropouts, `Still Enrolled` = still_enrolled) |>
  pivot_longer(cols = -end_year, names_to = "outcome", values_to = "count")

ggplot(dropout_long, aes(x = end_year, y = count, fill = outcome)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("Dropouts" = "#D32F2F", "Still Enrolled" = "#FF9800")) +
  labs(
    title = "Virginia Non-Graduates by Outcome (2019-2023)",
    subtitle = "Students who left high school without graduating",
    x = "Cohort Year",
    y = "Number of Students",
    fill = NULL
  )
```

---

## 11. Alexandria City High: one school, 1,138 seniors, 83% graduation

Alexandria City High School is Virginia's single largest high school by cohort, yet its 83.1% graduation rate trails the state average by nearly 9 points. As the only public high school in Alexandria City, every student funnels through one building.

```{r alexandria}
alex <- all_grad |>
  filter(is_school, diploma_type == "all",
         grepl("Alexandria City High", school_name)) |>
  select(end_year, school_name, cohort_size, graduation_rate, dropout_rate) |>
  mutate(grad_pct = round(graduation_rate * 100, 1))

alex
```

```{r alexandria-chart}
stopifnot(nrow(alex) > 0)

ggplot(alex, aes(x = end_year)) +
  geom_col(aes(y = cohort_size), fill = "#B0BEC5", alpha = 0.6) +
  geom_line(aes(y = graduation_rate * 1200), color = "#003366", linewidth = 1.2) +
  geom_point(aes(y = graduation_rate * 1200), color = "#003366", size = 3) +
  scale_y_continuous(
    name = "Cohort Size",
    labels = scales::comma,
    sec.axis = sec_axis(~ . / 1200, name = "Graduation Rate", labels = scales::percent)
  ) +
  labs(
    title = "Alexandria City High School (2019-2023)",
    subtitle = "Virginia's largest high school by cohort size",
    x = "Cohort Year"
  )
```

---

## 12. Fairfax County alone graduates 14,000 students per year

With 14,907 seniors in its 2023 cohort across 30 high schools, Fairfax County produces more graduates than many states. Its graduation rate has climbed from 91.3% in 2019 to 93.4% in 2023.

```{r fairfax-grad}
fairfax <- all_grad |>
  filter(is_school, diploma_type == "all",
         division_name == "Fairfax County") |>
  group_by(end_year) |>
  summarize(
    n_schools = n(),
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  ) |>
  mutate(grad_pct = round(grad_rate * 100, 1))

fairfax
```

```{r fairfax-grad-chart}
stopifnot(nrow(fairfax) > 0)

ggplot(fairfax, aes(x = end_year, y = grad_rate)) +
  geom_line(linewidth = 1.2, color = "#2E7D32") +
  geom_point(size = 3, color = "#2E7D32") +
  scale_y_continuous(labels = scales::percent, limits = c(0.88, 0.96)) +
  labs(
    title = "Fairfax County Graduation Rate (2019-2023)",
    subtitle = "30 high schools, 14,900+ seniors per year",
    x = "Cohort Year",
    y = "Graduation Rate"
  )
```

---

## 13. The biggest school-level improvements since 2019

Lancaster High School improved its graduation rate by 14 percentage points between 2019 and 2023 (from 83.8% to 97.8%). Armstrong High in Richmond jumped nearly 12 points.

```{r improvements}
improvement <- all_grad |>
  filter(is_school, diploma_type == "all", end_year %in% c(2019, 2023)) |>
  select(end_year, school_name, division_name, graduation_rate, cohort_size) |>
  pivot_wider(names_from = end_year, values_from = c(graduation_rate, cohort_size)) |>
  filter(!is.na(graduation_rate_2019), !is.na(graduation_rate_2023),
         cohort_size_2023 >= 50) |>
  mutate(change = round((graduation_rate_2023 - graduation_rate_2019) * 100, 1)) |>
  arrange(desc(change)) |>
  head(10)

improvement |>
  select(school_name, division_name, graduation_rate_2019, graduation_rate_2023,
         change, cohort_size_2023) |>
  mutate(
    rate_2019 = round(graduation_rate_2019 * 100, 1),
    rate_2023 = round(graduation_rate_2023 * 100, 1)
  )
```

```{r improvements-chart}
stopifnot(nrow(improvement) > 0)

improvement |>
  mutate(school_label = paste0(school_name, " (", division_name, ")"),
         school_label = forcats::fct_reorder(school_label, change)) |>
  ggplot(aes(x = change, y = school_label)) +
  geom_col(fill = "#4CAF50") +
  geom_text(aes(label = paste0("+", change, " pp")), hjust = -0.1, size = 3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    title = "Biggest Graduation Rate Improvements (2019 to 2023)",
    subtitle = "Schools with 50+ seniors in 2023 cohort",
    x = "Percentage Point Change",
    y = NULL
  )
```

---

## 14. Division-level graduation gap: 72% to 100%

Virginia's 130 school divisions span a 28-point graduation rate gap. Grayson County and Clarke County graduate nearly 100% of students, while Richmond City and Danville graduate fewer than 75%.

```{r division-gap}
div_grad <- all_grad |>
  filter(is_school, diploma_type == "all", end_year == 2023) |>
  group_by(division_name) |>
  summarize(
    cohort = sum(cohort_size, na.rm = TRUE),
    graduates = sum(total_graduates, na.rm = TRUE),
    grad_rate = graduates / cohort,
    .groups = "drop"
  ) |>
  filter(cohort >= 50)

cat("Top 5 divisions:\n")
div_grad |> arrange(desc(grad_rate)) |>
  head(5) |>
  mutate(grad_pct = round(grad_rate * 100, 1))

cat("\nBottom 5 divisions:\n")
div_grad |> arrange(grad_rate) |>
  head(5) |>
  mutate(grad_pct = round(grad_rate * 100, 1))
```

```{r division-gap-chart}
stopifnot(nrow(div_grad) > 0)

extremes <- bind_rows(
  div_grad |> arrange(desc(grad_rate)) |> head(5) |> mutate(group = "Top 5"),
  div_grad |> arrange(grad_rate) |> head(5) |> mutate(group = "Bottom 5")
)

extremes |>
  mutate(division_name = forcats::fct_reorder(division_name, grad_rate)) |>
  ggplot(aes(x = grad_rate, y = division_name, fill = group)) +
  geom_col() +
  scale_x_continuous(labels = scales::percent, limits = c(0, 1.05)) +
  scale_fill_manual(values = c("Top 5" = "#2E7D32", "Bottom 5" = "#D32F2F")) +
  labs(
    title = "Virginia Division Graduation Rates: Top and Bottom 5 (2023)",
    subtitle = "Among divisions with 50+ seniors",
    x = "Graduation Rate",
    y = NULL,
    fill = NULL
  )
```

---

## 15. Five years, 490,000 graduates

From 2019 to 2023, Virginia graduated 452,834 students across five cohorts totaling 490,872 seniors. The state maintains roughly 320 high schools.

```{r five-year-summary}
summary_stats <- all_grad |>
  filter(is_state, diploma_type == "all") |>
  summarize(
    years = n(),
    total_cohort = sum(cohort_size, na.rm = TRUE),
    total_graduates = sum(total_graduates, na.rm = TRUE),
    total_dropouts = sum(dropouts, na.rm = TRUE),
    avg_grad_rate = round(mean(graduation_rate) * 100, 1)
  )

summary_stats

school_counts <- all_grad |>
  filter(is_school, diploma_type == "all") |>
  group_by(end_year) |>
  summarize(n_schools = n_distinct(school_name), .groups = "drop")

school_counts
```

```{r five-year-summary-chart}
yearly_summary <- all_grad |>
  filter(is_state, diploma_type == "all") |>
  select(end_year, cohort_size, total_graduates)

stopifnot(nrow(yearly_summary) > 0)

yearly_long <- yearly_summary |>
  pivot_longer(cols = c(cohort_size, total_graduates),
               names_to = "measure", values_to = "count") |>
  mutate(measure = ifelse(measure == "cohort_size", "Cohort", "Graduates"))

ggplot(yearly_long, aes(x = end_year, y = count, fill = measure)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("Cohort" = "#B0BEC5", "Graduates" = "#003366")) +
  labs(
    title = "Virginia Cohort Size vs. Graduates (2019-2023)",
    subtitle = "490,000+ seniors over five years",
    x = "Cohort Year",
    y = "Number of Students",
    fill = NULL
  )
```

---

## Summary

Virginia's graduation data reveals:

- **Steady state rate**: 91.6%-93.0% graduation rate, well above the national average
- **Advanced Studies dominance**: More than half of graduates earn the rigorous Advanced Studies diploma
- **Richmond's challenge**: At 72%, the capital city lags the state by nearly 20 points
- **NoVA strength**: Loudoun County leads at 96.7%, but even Fairfax (93.4%) has risen steadily
- **Coalfield resilience**: Southwest Virginia divisions like Wise County (98.3%) outperform NoVA
- **COVID effect**: The 2021 cohort saw the highest graduation rate and lowest dropout rate
- **5,300 annual dropouts**: Virginia still loses thousands of students before graduation each year

---

## Data Notes

**Enrollment data source**: Virginia Department of Education (VDOE) School Quality Profiles

**Graduation data source**: VDOE Open Data Portal (Cohort Graduation and Dropout Report)

**Available years**: Enrollment 2016-2024 (9 years); Graduation 2019-2023 (5 years)

**Entities**: State, 132 school divisions (Virginia's term for districts), ~2,100 schools (enrollment), ~320 high schools (graduation)

**Enrollment subgroups**: Total enrollment, race/ethnicity (white, black, Hispanic, Asian, multiracial, Native American, Pacific Islander), gender

**Graduation data**: 4-year cohort graduation rate, dropout rate, completion rate, diploma types (Advanced Studies, Standard, IB, Applied Studies, GED, ISAEP, Certificate)

**Suppression**: Small counts suppressed for student privacy (marked as `<` in raw data, `NA` in processed data)

**Census Day**: Fall membership count (typically late September/early October)

**CAPTCHA note**: VDOE's School Quality Profiles site occasionally requires CAPTCHA verification for enrollment data. When this happens, use `use_cache = TRUE` (default) to rely on locally cached data. Graduation data is always available via the Open Data Portal.

---

*Data sourced from the Virginia Department of Education (VDOE).*

---

## Session Info

```{r session-info, eval=TRUE}
sessionInfo()
```
